### 2022-03-29 course/statml/2022/project/project.tex
project

@@

\lecture{Project 3: Final}{Yuan Yao}{Due: 23:59 Sunday 12 Dec, 2021}{18 Nov, 2021}

@@

\item For Kaggle contests, please register your team with name in the format of math6010z\_lastname, so that we could easily find your results on Kaggle. For example, a team with Shawn Zhu and Kate Wong would be named by math6010z\_Zhu\_Wong.

\item In the report, show your proposed scientific questions to explore and main results with a careful analysis supporting the results toward answering your problems. If possible, you should include your Kaggle contest score or rating in the report. Remember: scientific analysis and reasoning are more important than merely the performance tables. Separate source codes may be submitted through email as a GitHub link, or a zip file.    
\item Submit your report by email or paper version no later than the deadline, to the following address  (\href{mailto:aifin.hkust@gmail.com}{aifin.hkust@gmail.com}) with a title ``\underline{MATH6010z: Project 3}" % \#".  (\href{mailto:datascience.hw@gmail.com}{datascience.hw@gmail.com}) (\href{mailto:deeplearning.math@gmail.com}{deeplearning.math@gmail.com}) with Title: \underline{Math 6380P: Project 1}. % (\href{mailto:datascience\_hw@126.com}{datascience\_hw@126.com}).

@@

\section{Kaggle: G-Research Crypto Forecasting}

%\subsection{Project Overview}
Over USD40 billion worth of cryptocurrencies are traded every day. They are among the most popular assets for speculation and investment, yet have proven wildly volatile. Fast-fluctuating prices have made millionaires of a lucky few, and delivered crushing losses to others. Could some of these price movements have been predicted in advance?

In this competition, you'll use your machine learning expertise to forecast short term returns in 14 popular cryptocurrencies. We have amassed a dataset of millions of rows of high-frequency market data dating back to 2018 which you can use to build your model. Once the submission deadline has passed, your final score will be calculated over the following 3 months using live crypto data as it is collected.

\url{https://www.kaggle.com/c/g-research-crypto-forecasting}

%\subsection{Problem Identification}
%The cryptocurrency market has been skyrocketing recently, and it is estimated that over USD40 billion worth of cryptocurrencies are traded every single day. Cryptocurrencies have become one of the most popular and trending assets for speculation and investment, however, it has been proven to be wildly volatile, where a person can make a fortune and become a millionaire in one day, and lose all his assets the day after. While a few people have made a great fortune through the fast-fluctuating prices, others have been experiencing losses. Hence, we would like to try whether we can predict some of these price movements in advance and forecast short term returns in 14 popular cryptocurrencies through machine learning techniques.

\subsection{Background Knowledge}
The simultaneous activity of thousands of traders ensures that most signals will be transitory, persistent alpha will be exceptionally difficult to find, and the danger of overfitting will be considerable. In addition, since 2018, interest in the cryptomarket has exploded, so the volatility and correlation structure in our data are likely to be highly non-stationary. The successful contestant will pay careful attention to these considerations, and in the process gain valuable insight into the art and science of financial forecasting.

\subsection{Model and Methods}
Given a time-series based dataset of cryptocurrency prices, one can use the hierarchical time series model, which is to train a model for all time, models per weekday, model per day, etc. and ensemble them together. Multiple popular models could be applied and you might conduct research about the effectiveness of these models. For example, LSTM is popular among quantitative finance fields, as it can capture the relationship between previous cryptocurrency prices. Since cryptocurrency price is a time-dependent variable, multiple time-series prediction models may also be adopted, like traditional ARIMA, GARCH, and Dynamic linear model. You are welcome to create innovative methods, bringing more insights to the quantitative finance field.

\subsection{Data Source}
Kaggle link:

\url{https://www.kaggle.com/c/g-research-crypto-forecasting/data}

@@

    \begin{figure}
        \centering
        \includegraphics[width=.3\textwidth]{../project2/img/1.png}
        \hspace{0.5in}
        \includegraphics[width=.3\textwidth]{../project2/img/2.png}
        \caption{Examples of 20-day Image with volume bar and moving average line}
        \label{20-day image}
    \end{figure}

@@

    \begin{figure}
        \centering
        \includegraphics[width=.25\textwidth, height=0.45\textwidth]{../project2/img/cnn.png}
        \caption{Diagram of CNN model}
        \label{cnn model}
    \end{figure}

@@

\subsection{Empirical Asset Pricing via Machine Learning}

The requirements of this paper replication project are as follow:
\begin{itemize}
\item The machine learning methods used in this paper include linear regression (OLS, elastic net), dimension reduction (PLS, PCR), generalized linear models, trees (gradient boosting trees, random forest) and neural networks. Please try to replicate \textbf{at least 6 methods} of them (e.g., OLS, elastic net, PLS, PCR, random forest, neural networks, etc. Please note that if you choose OLS, OLS-3 should also be included; and if you choose neural network, NN1 to NN5 are included. Besides, robust loss function should also be considered. See details in the paper), and analyze your results specifically. Hints on parameter choice are presented in the paper.
\item Include the variable importance (section 2.3 of the paper) in your analysis. You do not need to replicate all the figures in section 2.3, but you are encouraged to investigate it carefully.
\item Note that this paper uses a `recursive performance evaluation scheme'. You are also required to evaluate your result by this method. For more details of this method, please refer to the paper and its supplementary material. The PPT presented in class about this project may also be helpful to you.
\item As you can know from the paper (section 2.1), predictive characteristics include firm characteristics, sic code and macroeconomic predictors. Firm characteristics and sic code are provided in the original dataset of this paper, and the 8 macroeconomic predictors are constructed following Welch and Goyal (2008), which are not directly provided in the original dataset of this paper. Hence, you may construct the predictors by yourself according to the description in Welch and Goyal (2008), for instance, see \\
\url{https://christophj.github.io/replicating/r/replicating-goyal-welch-2008/}.
\item The portfolio forecast part of the paper (section 2.4) is not compulsory for you to replicate.
\end{itemize}

\section{Kaggle Contest in Project 1: Home Credit Default Risk}

@@

@@

>>>>

\graphicspath{{img/}{../book.datasci/figures/}{../mySlides/figures/}}

@@

\lecture{Final Project}{Yuan Yao}{Due: 23:59 Monday 2 May, 2022}{23 Mar, 2022}

@@

\item For Kaggle contests, please register your team with name in the format of math5470\_lastname, so that we could easily find your results on Kaggle. For example, a team with Shawn Zhu and Kate Wong would be named by math5470\_Zhu\_Wong.

\item In the report, show your proposed scientific questions to explore and main results with a careful analysis supporting the results toward answering your problems. If possible, you should include your Kaggle contest score or rating in the report. Remember: scientific analysis and reasoning are more important than merely the performance tables. Separate source codes may be submitted through email as a GitHub link, or a zip file.    
\item Submit your report by email or paper version no later than the deadline, to the following address  (\href{mailto:aifin.hkust@gmail.com}{aifin.hkust@gmail.com}) with a title ``\underline{MATH5470: Final Project}" % \#".  (\href{mailto:datascience.hw@gmail.com}{datascience.hw@gmail.com}) (\href{mailto:deeplearning.math@gmail.com}{deeplearning.math@gmail.com}) with Title: \underline{Math 6380P: Project 1}. % (\href{mailto:datascience\_hw@126.com}{datascience\_hw@126.com}).

@@

\section{Kaggle Contest: Home Credit Default Risk}

\section{Kaggle Contest: M5 Forecasting}

How much camping gear will one store sell each month in a year? To the uninitiated, calculating sales at this level may seem as difficult as predicting the weather. Both types of forecasting rely on science and historical data. While a wrong weather forecast may result in you carrying around an umbrella on a sunny day, inaccurate business forecasts could result in actual or opportunity losses. In this competition, in addition to traditional forecasting methods you√ïre also challenged to use machine learning to improve forecast accuracy.

In this competition, you will use hierarchical sales data from Walmart, the world√ïs largest company by revenue, to forecast daily sales for the next 28 days and to make uncertainty estimates for these forecasts. The data, covers stores in three US States (California, Texas, and Wisconsin) and includes item level, department, product categories, and store details. In addition, it has explanatory variables such as price, promotions, day of the week, and special events. Together, this robust dataset can be used to improve forecasting accuracy.

%\section{Kaggle: G-Research Crypto Forecasting}
%
%%\subsection{Project Overview}
%Over USD40 billion worth of cryptocurrencies are traded every day. They are among the most popular assets for speculation and investment, yet have proven wildly volatile. Fast-fluctuating prices have made millionaires of a lucky few, and delivered crushing losses to others. Could some of these price movements have been predicted in advance?
%
%In this competition, you'll use your machine learning expertise to forecast short term returns in 14 popular cryptocurrencies. We have amassed a dataset of millions of rows of high-frequency market data dating back to 2018 which you can use to build your model. Once the submission deadline has passed, your final score will be calculated over the following 3 months using live crypto data as it is collected.
%
%\url{https://www.kaggle.com/c/g-research-crypto-forecasting}
%
%
%%\subsection{Problem Identification}
%%The cryptocurrency market has been skyrocketing recently, and it is estimated that over USD40 billion worth of cryptocurrencies are traded every single day. Cryptocurrencies have become one of the most popular and trending assets for speculation and investment, however, it has been proven to be wildly volatile, where a person can make a fortune and become a millionaire in one day, and lose all his assets the day after. While a few people have made a great fortune through the fast-fluctuating prices, others have been experiencing losses. Hence, we would like to try whether we can predict some of these price movements in advance and forecast short term returns in 14 popular cryptocurrencies through machine learning techniques.
%
%\subsection{Background Knowledge}
%The simultaneous activity of thousands of traders ensures that most signals will be transitory, persistent alpha will be exceptionally difficult to find, and the danger of overfitting will be considerable. In addition, since 2018, interest in the cryptomarket has exploded, so the volatility and correlation structure in our data are likely to be highly non-stationary. The successful contestant will pay careful attention to these considerations, and in the process gain valuable insight into the art and science of financial forecasting.
%
%\subsection{Model and Methods}
%Given a time-series based dataset of cryptocurrency prices, one can use the hierarchical time series model, which is to train a model for all time, models per weekday, model per day, etc. and ensemble them together. Multiple popular models could be applied and you might conduct research about the effectiveness of these models. For example, LSTM is popular among quantitative finance fields, as it can capture the relationship between previous cryptocurrency prices. Since cryptocurrency price is a time-dependent variable, multiple time-series prediction models may also be adopted, like traditional ARIMA, GARCH, and Dynamic linear model. You are welcome to create innovative methods, bringing more insights to the quantitative finance field.  
% 
%\subsection{Data Source}
%Kaggle link: 
%
%\url{https://www.kaggle.com/c/g-research-crypto-forecasting/data}

@@

    \begin{figure}
        \centering
        \includegraphics[width=.3\textwidth]{./img/1.png}
        \hspace{0.5in}
        \includegraphics[width=.3\textwidth]{./img/2.png}
        \caption{Examples of 20-day Image with volume bar and moving average line}
        \label{20-day image}
    \end{figure}

@@

    \begin{figure}
        \centering
        \includegraphics[width=.25\textwidth, height=0.45\textwidth]{./img/cnn.png}
        \caption{Diagram of CNN model}
        \label{cnn model}
    \end{figure}

@@

\section{Self-Proposed Projects}

\subsection{Kaggle Contest: Ubiquant Market Prediction}

Regardless of your investment strategy, fluctuations are expected in the financial market. Despite this variance, professional investors try to estimate their overall returns. Risks and returns differ based on investment types and other factors, which impact stability and volatility. To attempt to predict returns, there are many computer-based algorithms and models for financial market trading. Yet, with new techniques and approaches, data science could improve quantitative researchers' ability to forecast an investment's return.

Ubiquant Investment (Beijing) Co., Ltd is a leading domestic quantitative hedge fund based in China. In this competition, you’ll build a model that forecasts an investment's return rate. Train and test your algorithm on historical prices. Top entries will solve this real-world data science problem with as much accuracy as possible. The dataset contains features derived from real historic data from thousands of investments. Your challenge is to predict the value of an obfuscated metric relevant for making trading decisions.

@@

\url{https://www.kaggle.com/competitions/ubiquant-market-prediction}

@@

\subsection{Citi Bike System Data}

Where do Citi Bikers ride? When do they ride? How far do they go? Which stations are most popular? What days of the week are most rides taken on? We've heard all of these questions and more from you, and we're happy to provide the data to help you discover the answers to these questions and more. We invite developers, engineers, statisticians, artists, academics and other interested members of the public to use the data we provide for analysis, development, visualization and whatever else moves you.

\begin{itemize}
\item The following dataset: 
\begin{center}
\url{https://ride.citibikenyc.com/system-data},
\end{center}
\noindent is a famous open-source dataset about bike-sharing trips operated by Citi Bike Company. It offers daily information ranging from the start position, start time to end position, end time since 2013. It also contains some limited user information. The dataset is rich and comprehensive enough for us to conduct some machine learning projects.

\item A reference method: \url{https://arxiv.org/pdf/2109.14894.pdf}. We are planning to try the combination of neural processes and graph neural networks. Our lab has done a lot of works related to GNN but the research all focuses on algorithm performance. Uncertainty and reliability are ignored. Thus we want to refer to the aforementioned work, and based on this we may propose a well-designed algorithm for bike-sharing systems. We are curious to see whether more interesting insights or conclusions can be obtained concerning uncertainty analysis provided by Gaussian processes.
\end{itemize}

\subsection{Type-II diabetes and Alzheimer's disease}

This project is about the study on type-II diabetes and Alzheimer's Disease. It is confirmed that Type-II diabetes patient has higher risk of getting Alzheimer's disease
Research revealed that the brain connectivity strength changed in Type-II diabetes patients even before they showed impairment in cognition. MRI can collect the brain connectivity strength between each pair of brain regions. Therefore, it may enable us to explore the following scientific questions. Can we use brain connectivity features to distinguish type-II diabetes and healthy people in control group? Can we use brain connectivity features to predict clinical symptoms of type-II diabetes? With so many connectivity features, which are the top 5/10 features that contributed most to the classification and symptom prediction of type-II diabetes?

We will explore this question based on a dataset collected by No.1 Affiliated Hospital of GUCM which co-worked with WEI Yue. We have one under reviewing paper on this dataset, not published yet. For detailed description about this project, please refer to the following slides:

\noindent \url{https://yao-lab.github.io/course/statml/2022/slides/MATH\_5470\_probject\_intro\_MAR2022.pdf}
